A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-11 pilot-publication/lab-book.Rmd
Start comparing directly observed and retrospective data

>>>>

## Compare directly observed with retrospective data

```{r}
## Import data
data <- readr::read_csv(Sys.getenv("DATA_DIR"))

## Import codebook
codebook.arguments <- lapply(
    c("URL", "UID", "USERNAME", "PASSWORD"),
    function(x) Sys.getenv(paste0("KOBO_", x))
)
codebook <- do.call(noacsr::kobo_get_project_codebook, codebook.arguments)

## Prepare data
data <- prepare_data(data, codebook)

## Get variables to compare
retrospective.variables <- names(data)[grep("_r__", names(data), fixed = TRUE)]
directly.observed.variables <- retrospective.variables %>%
    stringr::str_replace_all(pattern = "\\_r\\_\\_", replacement = "\\_\\_") %>%
    stringr::str_replace_all(pattern = "\\_r$", replacement = "")

## Keep only observations with any retrospective data
data <- data[apply(data[, retrospective.variables], 1, function(row) any(!is.na(row))), ] %>%
    as_tibble()

## Extract retrospective and directly observed data
retrospective.data <- data[, retrospective.variables]
colnames(retrospective.data) <- directly.observed.variables
directly.observed.data <- data[, directly.observed.variables]
retrospective.data$collection.mode <- "Retrospective"
directly.observed.data$collection.mode <- "Directly observed"

## Make sure column classes are the same in both datasets
retrospective.data[] <- lapply(names(retrospective.data), function(column.name) {
    retrospective.column <- retrospective.data[[column.name]]
    directly.observed.column <- directly.observed.data[[column.name]]
    retrospective.class <- class(retrospective.column)
    directly.observed.class <- class(directly.observed.column)
    class.function <- paste0("as.", directly.observed.class)
    if ("POSIXct" %in% directly.observed.class) {
        class.function <- "as.POSIXct"
    }
    if (retrospective.class != directly.observed.class) {
        retrospective.column <- do.call(class.function, list(retrospective.column))
    }
    return(retrospective.column)
})

## Merge data
merged.data <- bind_rows(retrospective.data, directly.observed.data)
```
